### 2015-01-16 src/analysis.Rnw
add Mutation details

>>>>

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
bcol <- '#2171B5'
icol <- '#9ECAE0'
m.db <- subset(allmutants.db, total > 0)
d.db <- subset(allmutants.db, detected > 0)
m.db$mutations <- m.db$mtotal * 100.0 / m.db$total
d.db$detected <- d.db$mdetected * 100.0 / d.db$detected

tmp1 <- subset(m.db, select=c("mutator","mutations"))
tmp1$type <- "mutations"
tmp2 <- subset(d.db, select=c("mutator","detected"))
colnames(tmp2) <- c("mutator","mutations")
tmp2$type <- "detected"
tmp <- rbind(tmp1, tmp2)
tmp$type <- factor(tmp$type, levels=c("mutations", "detected"))
tmp$mutator <- factor(tmp$mutator, levels=c("nmc", "rv", "ic", "dc", "nc", "rc", "vmc", "cc", "emv", "m", "cb", "i", "ri", "rs", "es", "in"))
options(warn=-1)
ggplot(aes(y=mutations, x=mutator, fill=type),data=tmp) +
  geom_boxplot(outlier.color=NA, outlier.shape=NA) +
  scale_fill_manual(name = "Mutation Details", values = c(bcol, icol)
                    , labels = c("mutations" = "Total mutations", "detected" = "Detected mutations")) +
 theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
 theme(axis.line = element_line(colour = "black"))
 # coord_flip() +
options(warn=0)
# + stat_boxplot(geom ='errorbar') 
#p1 <- ggplot(aes(y=mutations, x=mutator, fill=F),data=m.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()
#p2 <- ggplot(aes(y=detected, x=mutator, fill=F),data=d.db) + geom_boxplot() + guides(fill=FALSE) + coord_flip()

#grid.newpage()
#pushViewport(viewport(layout = grid.layout(1, 2)))
#print(p1, vp = vplayout(1, 1))
#print(p2, vp = vplayout(1, 2))

@
\caption{The relative contribution of mutation operators in terms of fraction of mutants produced and detected. The produced mutants are shown with black outline while detected mutants have blue border and shade.}
\end{figure*}

### 2015-01-16 src/paper.Rnw
update
add Mutation details

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(scales)
require(xtable)
require(ggplot2)
require(MutSel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='MutSel')
data(list = v$results[,3])
@
\end{comment}
<<>>=

>>>>

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(scales)
require(xtable)
require(ggplot2)
require(grid)
require(MutSel)
vplayout <- function(x, y) viewport(layout.pos.row = x, layout.pos.col = y)
theme = theme_set(theme_minimal())
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='MutSel')
data(list = v$results[,3])
@
\end{comment}
<<>>=
